DOpElib:\\ Differential Equations and Optimization Environment

### 2019-04-24 Examples/PDE/StatPDE/Example16/content.tex
Added error estimation for obstacle problem

>>>>

 Further, in this example we show a residual based error estimator
 for the obstacle problem, as given in~\cite{Walloth:2017}. In
 principle this is similar to the calculations needed in
 Example~\ref{PDE_adap_Stat_Laplace}, i.e., defining the
 \texttt{Strong*Residual} terms in the \texttt{LocalPDE} class.
 However, for the estimate of the obstacle we need too special
 information. First, for a given vertex $x_i$, we need to know if
 $x_i$ is a \textit{full contact} node, meaning that $u = \chi$ on
 $\omega_i = \cup_{T \mid x_i \in T} T$ the patch around $v$. Further,
 we need to have $|\omega_i| = \int_{\omega_i} \phi_i\,\mathrm{d}x$ for all
 vertices to correctly scale the complementarity residual.
 Unfortunately, both data are non-local, i.e., we can not compute it
 on any given $T$ alone.

 However, we can compute these values if we have one additional
 integration over the domain. I.e. to get $|\omega_i|$ we simply
 define a function $\omega \in \mathcal Q_1$ by $\omega(v) = \omega_v$
 which we can calculate by computing the nodal vector corresponding to
 the functional
 \[
   \int_\Omega \phi\,\mathrm{d}x.
 \]
 In a similar manner, we can calculate if a vertex is in full contact
 by adding $1$ to a nodal vector whenever its support is contained in
 a full contact element, and rescaling with the number of elements
 adjacent to the corresponding node.

 To execute these computations the \texttt{ObstacleResidualErrorContainer}
 has a function \texttt{NPrecomputedNodalValues} returning $1$ since we
 can compute both vectors in a single integration. The actual
 integration is then implemented in \texttt{LocalPDE} in the
 \texttt{*AuxRhs} which will be evaluated prior to error estimation.
 The results are then accessible via the vector
 \texttt{aux\_errror\_0} from the \texttt{*DataContainers} in the
 evaluation of the \texttt{Strong*Residual}.

 Note, if more than one precomputation is requested the results will
 be accessible in \texttt{aux\_error\_i} for an appropriate index $i$.
